### 2018-07-25 express2018/conclusions.tex
There're still typos (found by spellchecker), amazing...

We have highlighted a formalisation of the theory of CCS in the 
HOL4 theorem prover (for lack of space we have not discussed 
the formalisation of some basic algebraic theory, of the basic
properties of the expansion preorder,   and of a few
 versions of `bisimulation up to'
techniques). % such as  bisimulation up-to bisimilarity). 
The formalisation has focused on the theory of
unique solution of equations and contractions. 
It has also allowed us to further develop the theory,
notably the basic properties of rooted contraction, and the unique
solution theorem for it with respect to rooted bisimilarity. 
The formalisation brings up and exploits similarities between results
and proofs for different equivalences and preorders. 
We think that the statements in the formalisation are easy to read and
understand, as they are very close to the orginal statements found in
standard CCS textbooks \cite{Gorrieri:2015jt,Mil89}.

For the future work, it would be worth extending the current work
to multi-variable equations/contractions. \hl{Preliminary work shows that,
a key aspect could be using unguarded constants as free variables
(\texttt{FV}) and define guardness directly on type CCS (instead of CCS
$\rightarrow$ CCS) then connect to previous context:}
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{weakly_guarded1} \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X}. \HOLBoundVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e}. \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{e} (\HOLConst{var} \HOLBoundVar{X}) \HOLSymConst{=} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \HOLBoundVar{e}
\end{alltt}

@@

% We believe that, beside the discovery of the rooted contraction $\rcontr$
% with a more elegant unique solution theorem,
% our CCS formalisation in HOL4 has also
% provided a solid formal framework for future theoretical developments in
% Concurrency Theory, particularily for process algebras like CCS. It's
% easily understandable, with statements extremely close to the original
% textbook. The logic foundations of HOL makes the whole work (or individual
% parts) easily portable to other theorem provers.

@@

We have benefitted from suggestions and comments 
from several people from the HOL
community, including (in alphabet order) Robert Beers, Jeremy Dawson,
Ramana Kumar,
Michael Norrish, 
Konrad Slind, and
Thomas Tuerk.
%
The second half of this
paper was written in memory of Mike J. Gordon, the creator of HOL theorem prover.

>>>>

We have highlighted a formalisation of the theory of CCS in the 
HOL4 theorem prover (for lack of space we have not discussed 
the formalisation of some basic algebraic theory, of the basic
properties of the expansion preorder,   and of a few
 versions of `bisimulation up to'
techniques). % such as  bisimulation up-to bisimilarity). 
The formalisation has focused on the theory of
unique solution of equations and contractions. 
It has also allowed us to further develop the theory,
notably the basic properties of rooted contraction, and the unique
solution theorem for it with respect to rooted bisimilarity. 
The formalisation brings up and exploits similarities between results
and proofs for different equivalences and preorders. 
We think that the statements in the formalisation are easy to read and
understand, as they are very close to the original statements found in
standard CCS textbooks \cite{Gorrieri:2015jt,Mil89}.

For the future work, it would be worth extending the current work
to multi-variable equations/contractions. \hl{Preliminary work shows that,
a key aspect could be using unguarded constants as free variables
(\texttt{FV}) and define guardedness directly on type CCS (instead of CCS
$\rightarrow$ CCS) then connect to previous context:}
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{weakly_guarded1} \HOLFreeVar{E} \HOLSymConst{\HOLTokenEquiv{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{X}. \HOLBoundVar{X} \HOLSymConst{\HOLTokenIn{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenImp{}} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e}. \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenConj{}} (\HOLBoundVar{e} (\HOLConst{var} \HOLBoundVar{X}) \HOLSymConst{=} \HOLFreeVar{E}) \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \HOLBoundVar{e}
\end{alltt}

@@

% We believe that, beside the discovery of the rooted contraction $\rcontr$
% with a more elegant unique solution theorem,
% our CCS formalisation in HOL4 has also
% provided a solid formal framework for future theoretical developments in
% Concurrency Theory, particularly for process algebras like CCS. It's
% easily understandable, with statements extremely close to the original
% textbook. The logic foundations of HOL makes the whole work (or individual
% parts) easily portable to other theorem provers.

@@

We have benefitted from suggestions and comments 
from several people from the HOL
community, including (in alphabet order) Robert Beers, Jeremy Dawson,
Ramana Kumar,
Michael Norrish, 
Konrad Slind, and
Thomas T\"{u}rk.
%
The second half of this
paper was written in memory of Mike J. Gordon, the creator of HOL theorem prover.

### 2018-07-25 express2018/context.tex
There're still typos (found by spellchecker), amazing...

We have chosen to use $\lambda$-expressions (\hl{with the type}
``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'')
to represent \emph{multi-hole contexts}.
%
\hl{This choice has a significant advantage over \emph{one-hole
contexts}, as each hole corresponds to one
appearence of the \emph{same} variable in single-variable
expressions (or equations). Thus \emph{contexts} can be directly used in
formulating the unique solution of equations theorems in
single-variable cases.} The precise definition is given inductively:
\begin{alltt}
\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[CONTEXT_rules]}
\end{alltt}

>>>>

We have chosen to use $\lambda$-expressions (\hl{with the type}
``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS}}'')
to represent \emph{multi-hole contexts}.
%
\hl{This choice has a significant advantage over \emph{one-hole
contexts}, as each hole corresponds to one
appearance of the \emph{same} variable in single-variable
expressions (or equations). Thus \emph{contexts} can be directly used in
formulating the unique solution of equations theorems in
single-variable cases.} The precise definition is given inductively:
\begin{alltt}
\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t})
\HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{p})
\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{a}\HOLSymConst{..}\HOLFreeVar{e} \HOLBoundVar{t})
\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
\HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLFreeVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\parallel}} \HOLFreeVar{e\sb{\mathrm{2}}} \HOLBoundVar{t})
\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLSymConst{\ensuremath{\nu}} \HOLFreeVar{L} (\HOLFreeVar{e} \HOLBoundVar{t}))
\HOLConst{CONTEXT} \HOLFreeVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} (\HOLFreeVar{e} \HOLBoundVar{t}) \HOLFreeVar{rf})\hfill{[CONTEXT_rules]}
\end{alltt}

### 2018-07-25 express2018/formal.tex
There're still typos (found by spellchecker), amazing...

HOL4 is written in Standard ML, a single programming language who
plays three different roles:
%(The situation is quite different in other systems like Coq\footnote{\hl{The Coq Proof Assistant.} \url{https://coq.inria.fr}}.)
\begin{enumerate}
\item It serves as the underlying implementation language for the core HOL engine;
\item it is used to implement tactics (and tacticals) for writing proofs;
\item it is used as the command language of the HOL interactive shell.
\end{enumerate}
\hl{Moreover, using} the same language HOL4 users can write complex automatic
verification tools by calling HOL's interactive theorem proving
facilities. \hl{(The formal proof of theorems in CCS theory
is mostly done by an \emph{interactive process} closely following
their informal proofs.)}

@@

\emph{In this
formalisation we consider only single-variable equations/contractions.}
This considerably
 simplifies the required proofs in HOL, enhances the readibility of
 proof scripts, \hl{without loss of generality (for paper proofs, the
 general case is just a routine
 adaptation).}
%   still aligned with
% their informal proofs.
%  (on 
% the extension  to multiple equations/contractions
% see also  Section~\ref{s:concl}).

>>>>

HOL4 is written in Standard ML, a single programming language who
plays three different roles:
%(The situation is quite different in other systems like Coq\footnote{\hl{The Coq Proof Assistant.} \url{https://coq.inria.fr}}.)
\begin{enumerate}
\item It serves as the underlying implementation language for the core HOL engine;
\item it is used to implement tactics (and tacticals) for writing proofs;
\item it is used as the command language of the HOL interactive shell.
\end{enumerate}
\hl{Moreover, using} the same language HOL4 users can write complex automatic
verification tools by calling HOL's theorem proving
facilities. \hl{(The formal proofs of theorems in CCS theory
are mostly done by an \emph{interactive process} closely following
their informal proofs, with minimal automatic proof searching.)}

@@

\emph{In this
formalisation we consider only single-variable equations/contractions.}
This considerably
 simplifies the required proofs in HOL, enhances the readability of
 proof scripts, \hl{without loss of generality (for paper proofs, the
 general case is just a routine
 adaptation).}
%   still aligned with
% their informal proofs.
%  (on 
% the extension  to multiple equations/contractions
% see also  Section~\ref{s:concl}).

### 2018-07-25 express2018/intro.tex
There're still typos (found by spellchecker), amazing...

In the versions of Milner's unique solution theorems for proving that all
solutions are weakly (or rooted) bisimilar (in practice these are the most
relevant cases), however,
Milner's proof method has severe syntactical limitations, such that
the equations must be ``guarded and sequential,'' that is, the
variables of the equations may only be used underneath a visible
prefix and preceed, in the syntax tree, only by the sum and prefix operators.
One way of overcoming such limitations is to replace equations
 with special inequations called
\emph{contractions} \cite{sangiorgi2015equations,sangiorgi2017equations}. Contraction is a
preorder that, roughly, places some efficiency
constraints on processes.  The uniqueness of solutions of a system of contractions
is defined as with systems of equations: any two solutions must be bisimilar.
The difference with equations is in the meaning of a solution:
in the case of contractions the solution is evaluated with respect to
the contraction preorder, rather than bisimilarity. 
With contractions, most syntactic limitations of the unique-solution theorem can be
removed.  One constraint that still remains in
\cite{sangiorgi2017equations} (in which the issue is bypassed using a more
restrictive CCS syntax)
is the occurrences of direct sums, due to the failure of the
substitutivity of contraction under direct sums.

>>>>

In the versions of Milner's unique solution theorems for proving that all
solutions are weakly (or rooted) bisimilar (in practice these are the most
relevant cases), however,
Milner's proof method has severe syntactical limitations, such that
the equations must be ``guarded and sequential,'' that is, the
variables of the equations may only be used underneath a visible
prefix and proceed, in the syntax tree, only by the sum and prefix operators.
One way of overcoming such limitations is to replace equations
 with special inequations called
\emph{contractions} \cite{sangiorgi2015equations,sangiorgi2017equations}. Contraction is a
preorder that, roughly, places some efficiency
constraints on processes.  The uniqueness of solutions of a system of contractions
is defined as with systems of equations: any two solutions must be bisimilar.
The difference with equations is in the meaning of a solution:
in the case of contractions the solution is evaluated with respect to
the contraction preorder, rather than bisimilarity. 
With contractions, most syntactic limitations of the unique-solution theorem can be
removed.  One constraint that still remains in
\cite{sangiorgi2017equations} (in which the issue is bypassed using a more
restrictive CCS syntax)
is the occurrences of direct sums, due to the failure of the
substitutivity of contraction under direct sums.

### 2018-07-25 express2018/part2.tex
There're still typos (found by spellchecker), amazing...

The definition of ``unique label'' \hl{can be done in many ways, the
following definition (a suggestion from Robert Beers)
avoides any counting or filtering in the list.}
It says that a label is unique in a list of actions if and only if there is no
label in the rest of list:
\begin{alltt}
\HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLFreeVar{L} \HOLSymConst{\HOLTokenEquiv{}}
\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{L\sb{\mathrm{1}}} \HOLBoundVar{L\sb{\mathrm{2}}}. (\HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDoublePlus} [\HOLFreeVar{u}] \HOLSymConst{\HOLTokenDoublePlus} \HOLBoundVar{L\sb{\mathrm{2}}} \HOLSymConst{=} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{2}}}\hfill{[UNIQUE_LABEL_def]}
\end{alltt}

>>>>

The definition of ``unique label'' \hl{can be done in many ways, the
following definition (a suggestion from Robert Beers)
avoids any counting or filtering in the list.}
It says that a label is unique in a list of actions if and only if there is no
label in the rest of list:
\begin{alltt}
\HOLConst{UNIQUE_LABEL} \HOLFreeVar{u} \HOLFreeVar{L} \HOLSymConst{\HOLTokenEquiv{}}
\HOLSymConst{\HOLTokenExists{}}\HOLBoundVar{L\sb{\mathrm{1}}} \HOLBoundVar{L\sb{\mathrm{2}}}. (\HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenDoublePlus} [\HOLFreeVar{u}] \HOLSymConst{\HOLTokenDoublePlus} \HOLBoundVar{L\sb{\mathrm{2}}} \HOLSymConst{=} \HOLFreeVar{L}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{NO_LABEL} \HOLBoundVar{L\sb{\mathrm{2}}}\hfill{[UNIQUE_LABEL_def]}
\end{alltt}

### 2018-07-25 express2018/related.tex
There're still typos (found by spellchecker), amazing...

\hl{Monica Nesi made the first CCS formalisations for both pure and
value-passing CCS} \cite{Nesi:1992ve,Nesi:2017wo} using early versions of the HOL
theorem prover.\footnote{Part of her old proof scripts is now available at
  \url{https://github.com/binghe/HOL-CCS/tree/master/CCS-Nesi}.}
Her main focus was on implementing decision procedures (as a ML
program, e.g.~\cite{cleaveland1993concurrency}) for
automatically proving bisimilarities of CCS
processes. %, thus she stopped proving deeper theorems in Milner's
           %book, once the congruence and algebraic laws of 
%strong, weak and rooted bisimilarity were proved.
\hl{Her work is
  the working basis of ours. However, the differences are substantial, especially in the way of defining
bisimilarities. We greatly benefited from features and standard
libraries in recent versions of HOL4, and our formalisation has
covered a much larger spectrum of the (pure) CCS theory.}

>>>>

\hl{Monica Nesi did the first CCS formalisations for both pure and
value-passing CCS} \cite{Nesi:1992ve,Nesi:2017wo} using early versions of the HOL
theorem prover.\footnote{Part of her old proof scripts is now available at
  \url{https://github.com/binghe/HOL-CCS/tree/master/CCS-Nesi}.}
Her main focus was on implementing decision procedures (as a ML
program, e.g.~\cite{cleaveland1993concurrency}) for
automatically proving bisimilarities of CCS
processes. %, thus she stopped proving deeper theorems in Milner's
           %book, once the congruence and algebraic laws of 
%strong, weak and rooted bisimilarity were proved.
\hl{Her work is
  the working basis of ours. However, the differences are substantial, especially in the way of defining
bisimilarities. We greatly benefited from features and standard
libraries in recent versions of HOL4, and our formalisation has
covered a much larger spectrum of the (pure) CCS theory.}

### 2018-07-25 express2018/sos.tex
There're still typos (found by spellchecker), amazing...

The rule \texttt{REC} (Recursion)
 says that if we substitute all appearances of variable $A$ in $P$ to
$(\mathbf{rec}\; A\; P)$ and the resulting process has a transition to $P'$
with action $u$, then $(\mathbf{rec}\; A\; P)$ has the same
transition. From HOL's viewpoint, these
SOS rules are \emph{inductive 
  definitions} on the 3-ary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL's 
\texttt{Hol_reln} function.

A useful function that we have defined, exploiting the interplay
between HOL4 and Standard ML (and following an idea by Nesi \cite{Nesi:1992ve})
 is a complex Standard ML function
  taking a CCS process and returning a theorem indicating all its
  direct transitions.\footnote{If the input process could yield
    something infinite branching, due to the use of recursion or
    relabeling operators, the program will loop forever without
    outputing a theorem.}
For instance, we know that the process $(a.0 | \bar{a}.0)$ has three
possible transitions: $(a.0 | \bar{a}.0) \overset{a}{\longrightarrow}
(0 | \bar{a}.0)$, $(a.0 | \bar{a}.0)
\overset{\bar{a}}{\longrightarrow} (a.0 | 0)$ and $(a.0 | \bar{a}.0)
\overset{\tau}{\longrightarrow} (0 | 0)$.
To completely describe all possible transitions of a process, if done manually, the
following facts should be proved: (1) there exists transitions from
$(a.0 | \bar{a}.0)$ (optional); (2) the correctness for each of the
transitions; and (3) the non-existence of other transitions.

>>>>

The rule \texttt{REC} (Recursion)
 says that if we substitute all appearances of variable $A$ in $P$ to
$(\mathbf{rec}\; A\; P)$ and the resulting process has a transition to $P'$
with action $u$, then $(\mathbf{rec}\; A\; P)$ has the same
transition. From HOL's viewpoint, these
SOS rules are \emph{inductive 
  definitions} on the tenary relation \HOLinline{\HOLConst{TRANS}} of type ``\HOLinline{(\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{\beta} \HOLTyOp{Action} \HOLTokenTransEnd (\ensuremath{\alpha}, \ensuremath{\beta}) \HOLTyOp{CCS} \HOLTokenTransEnd \HOLTyOp{bool}}'', generated by HOL's 
\texttt{Hol_reln} function.

A useful function that we have defined, exploiting the interplay
between HOL4 and Standard ML (and following an idea by Nesi \cite{Nesi:1992ve})
 is a complex Standard ML function
  taking a CCS process and returning a theorem indicating all its
  direct transitions.\footnote{If the input process could yield
    something infinite branching, due to the use of recursion or
    relabeling operators, the program will loop forever without
    outputting a theorem.}
For instance, we know that the process $(a.0 | \bar{a}.0)$ has three
possible transitions: $(a.0 | \bar{a}.0) \overset{a}{\longrightarrow}
(0 | \bar{a}.0)$, $(a.0 | \bar{a}.0)
\overset{\bar{a}}{\longrightarrow} (a.0 | 0)$ and $(a.0 | \bar{a}.0)
\overset{\tau}{\longrightarrow} (0 | 0)$.
To completely describe all possible transitions of a process, if done manually, the
following facts should be proved: (1) there exists transitions from
$(a.0 | \bar{a}.0)$ (optional); (2) the correctness for each of the
transitions; and (3) the non-existence of other transitions.

### 2018-07-25 express2018/unique.tex
There're still typos (found by spellchecker), amazing...

\hl{The precise formulation of  this definition was guided by the HOL theorem
  prover and
the following two principles:} (1) the definition should not be recursive,
along the lines of rooted bisimilarity
$\approx^c$ in Def.~\ref{d:rootedBisimilarity};
(2) the definition should  be built on top of existing \emph{contraction}
relation $\mcontrBIS$ (because of its completeness). 
\hl{A few other candicates were quickly tested and rejected, e.g.,
  because of  precongruence issue.} The proof of the precongruence
 result below is along the lines of the analogous result
for rooted bisimilarity with respect to bisimilarity.

>>>>

\hl{The precise formulation of  this definition was guided by the HOL theorem
  prover and
the following two principles:} (1) the definition should not be recursive,
along the lines of rooted bisimilarity
$\rapprox$ in Def.~\ref{d:rootedBisimilarity};
(2) the definition should  be built on top of existing \emph{contraction}
relation $\mcontrBIS$ (because of its completeness). 
\hl{A few other candidates were quickly tested and rejected, e.g.,
  because of  precongruence issue.} The proof of the precongruence
 result below is along the lines of the analogous result
for rooted bisimilarity with respect to bisimilarity.
